---
title: "Lab 03 - Nobel laureates"

author: "Tianchang_Lu, HaoyuanZhu, Vangeli_Porfyris, Qimiao_Li, Loizos "


date: "`r Sys.Date()`"
output: html_document
---


### Load packages and data

```{r load-packages, message = FALSE, warning=FALSE}
library(tidyverse) 
```

```{r reading-nobel-data, message = FALSE}
nobel <- read_csv("data/nobel.csv")
```

### Exercise 1
count(nobel)
#### Narrative

There are 935 observations, and 25 variables and each row represents a different nobel prize, meaning the same person can recieve it twice.


### Exercise 2

#### Code

```{r nobel-living}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*


### Exercise 3

#### Code

```{r facet-bar-plot}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*


### Exercise 4

#### Code

```{r born-country-us}
# remove this comment and add your code here
```


### Exercise 5

#### Narrative

*Remove this text and add your answer here.*

#### Code

```{r facet-bar-plot-redo}
# remove this comment and add your code here
```


### Exercise 6

#### Code

```{r born-country}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*